---
title: "Live Session Unit 5 Assignment"
author: "Martin"
date: "September 27, 2018"
output: html_document
---



* Required Libraries
  +dplyr
  
Can also be found at the repo below:
https://github.com/martin8886/Homework



#1 Data Munging

##a.

We read our data using a semicolon as our separator and assign specific column names.

* Names
* Gender
* Qty_Children

```{r echo=TRUE}
library("dplyr")

df <- read.table("yob2016.txt", sep=";", header=FALSE)
names(df) <- c("Names", "Gender", "Qty_Children")
```

##b.

Summary and structure of our data

```{r echo=TRUE}
summary(df)
str(df)
```

##c. 

Grep pulls our name of interest.

```{r echo=TRUE}
grep("yyy$",df$Names, value=TRUE)
```


##d.

We remove the name of interest

```{r ech=TRUE}
y2016 <- filter(df, Names != "Fionayyy")
```

#2 Data Merging

##a.

We read our data using a comma as our separator and assign the same names for our columns.

```{r echo=TRUE}

y2015 <- read.table("yob2015.txt", sep=",", header=FALSE)
names(y2015) <- c("Names", "Gender", "Qty_Children")
```

##b. 

Using the tail function we observe names that start with Z tend to be male.

```{r echo=TRUE}
tail(y2015, 10)
```

##c.

Finally we combine both dataframes only keeping those with shared values using the transmute function.

```{r echo=TRUE}
final <- merge(x=y2016, y=y2015, by="Names")
final <- transmute(final,  Names = Names, Gender = Gender.x, Quantity = Qty_Children.x + Qty_Children.y)
```

#3. Data Summary

##a.

We use our transmute to create a new dataframe using existing data and name it final.

Sum function determines the total number of people with popular names.

```{r echo=TRUE}
final <- transmute(final,  Names = Names, Gender = Gender, Total = Quantity)
sum(final$Total)

```

b.

```{r echo=TRUE}
final <- final[with(final, order(Total, Names, Gender, decreasing = TRUE)),]

#With head set to 10 we can see the top 10 names
head(final, 10)
```

c.

We subset our dataframe to include everything but males.

```{r echo=TRUE}

final <- subset(x=final, Gender != "M")
head(final, 10)

```

d.

We save our top 10 list of female names as a csv file.

```{r echo=TRUE}
write.csv(final[1:10,1],'TopTenFemaleNames.csv')
```
